|

### 2023-02-06 manuscript/manuscript.Rmd
more editing

The conditional expected value of the combined outcome in Equation (\ref{eq:combinedOutcome}) is given by
\begin{align*}
  E[\widetilde{Y} \mid R, X] = E[Y \mid R, X, A=1]P(A = 1 \mid R, X) + \mathcal{E}P(A = 0 \mid R, X)
\end{align*}
From this expression one can show that a treatment comparison expressed in terms of a contrast of the expectation of $\widetilde{Y}$ can be zero even though the distribution of $((Y \mid A=1), A)$  depends on $R$. To see this, let $E[Y \mid A=1, R = 0, X] = \mu(X)$ and $E[Y \mid A=1, R = 1, X] = \mu(X) + \mu_{\delta}(X)$ and assume without loss of generalization that $\mathcal{E} = 0$. Then the average treatment effect for the combined outcome conditional on baseline covariates is 
\begin{align}
  \Delta(X) &= E[\widetilde{Y} \mid R = 1, X] - E[\widetilde{Y} \mid R = 0, X]\label{eq:Delta}\\
        &= \mu(X)\left[P(A = 1 \mid R=1,X) - P(A = 1 \mid R = 0, X)\right] + \mu_{\delta}(X) P(A = 1 \mid R = 1, X)\nonumber
\end{align}
If we auspiciously let $\mu_{\delta}(X) = \mu(X)\left[P(A = 1 \mid R = 0, X) P(A = 1 \mid R = 1, X)^{-1} - 1\right]$ then $\Delta(X) = 0$ for all values of $X$ even though $\mu_{\delta}(X) \ne 0$ and $P(A = 1 \mid R = 0, X) \ne P(A = 1 \mid R = 1, X)$. On the other hand, if $\mu_\delta(X) = 0$ and $P(A = 1 \mid R=1,X) = P(A = 1 \mid R = 0, X)$ then $\Delta(X)$ is necessarily equal to zero. This illustrates that a significance test of no treatment effect must have two degrees of freedom. Such a test which we develop in the subsequent sections is conceptually difference than a test for the null hypothesis $\Delta(X) = 0$. Noe that in RCTs one would typically not include any variables $X$ since these are balanced by design.

We propose to test the null hypothesis of no treatment effect on the combined outcome by a likelihood ratio test of the joint distribution of $Y_i \mid A_i$ and $A_i$. This has the advantage that it increases the efficiency compared the Wilcoxon test and it yields a single p-value appropriate for testing a primary outcome in a clinical trial. Let $(Y_i, A_i, R_i, X_i)$ for $i = 1, \ldots, n$ be independent and identically distributed random variables. We can write our model in a general form as 
\begin{align*}
  Y_i \mid A_i = 1, R_i, X_i &\sim F(Y_i; \mu_i(R_i, X_i), \Psi)\\
  A_i \mid R_i, X_i &\sim \text{Bernoulli}(A_i; \pi_i(R_i, X_i))  
\end{align*}
for some mean functions $\pi_i$ and $\mu_i$ and a distribution function $F$ characterizing the distribution of the observed continuous outcomes with possible nuisance parameter $\Psi$. The joint likelihood function for the combined outcome conditional on treatment and baseline covariates is
\begin{align*}
 L_n(\mu_i(R_i, X_i), \pi_i(R_i, X_i), \Psi) &= \prod_{i=1}^n f(Y_i; \mu_i(R_i, X_i), \Psi)^{A_i}P(A_i = a_i; \pi_i(R_i, X_i))\\
     &= \prod_{i=1}^n f(Y_i; \mu_i(R_i, X_i), \Psi)^{A_i} \pi_i(R_i, X_i)^{A_i} (1 - \pi_i(R_i, X_i))^{1-A_i}\nonumber
\end{align*}
We note that when $F$ admits an absolutely continuous density function the likelihood function can equivalently be written solely in terms of the combined outcome $\widetilde{Y}$ in Equation (\ref{eq:combinedOutcome}) since $f(Y_i; \cdot)^{A_i} = f(\widetilde{Y}_i; \cdot)^{\mathbbm{1}(\widetilde{Y}_i \ne \mathcal{E})}$ and $\pi_i(\cdot)^{A_i} = \pi_i(\cdot)^{\mathbbm{1}(\widetilde{Y}_i \ne \mathcal{E})}$ almost surely. An important property of this model is that the likelihood function then factorizes into two components as
\begin{align}
 L_n(\mu_i(R_i, X_i), \pi_i(R_i, X_i)) &= L_{1,n}(\mu_i(R_i, X_i), \Psi) L_{2,n}(\pi_i(R_i, X_i))\label{eq:likFactorization}
\end{align}
where $L_{1,n}(\mu_i(R_i, X_i), \Psi) = \prod_{i=1}^n f(Y_i; \mu_i(R_i, X_i), \Psi)^{A_i}$ and $L_{2,n}(\pi_i(R_i, X_i)) = \prod_{i=1}^n \pi_i(R_i, X_i)^{A_i} (1 - \pi_i(R_i, X_i))^{1-A_i}$. This implies that the parameters for the observed outcomes, $\mu_i(R_i, X_i)$, can be estimated independently of the parameters governing the probability of observing the outcome, $\pi_i(R_i, X_i)$. This factorization is a consequence of the likelihood construction and it does neither assume nor require independence between the value of the outcome and the probability of observing it.

Under the assumption of generalized linear models for $\mu_i(R_i, X_i)$ and $\pi_i(R_i, X_i)$ with additive structures we may parametrize the mean functions as
\begin{align}
  \E[Y_i \mid A_i = 1, R_i, X_i] &= \mu_0 + \mu_{\delta} R_i + s_\mu(X_i)\label{eq:glm1}\\
  \logit P(A_i = 1 \mid R_i, X_i) &= \beta_0 + \beta_{\delta} R_i + s_\beta(X_i)\label{eq:glm2}
\end{align}
where the treatment effect is quantified by bi-variate contrast $(\mu_\delta, \beta_\delta)$ and $s_\mu, s_\beta\colon\, \mathbb{R}^p \mapsto \mathbb{R}$ are some models for the baseline covariates. The parameter $\mu_\delta$ is interpreted as the expected difference among the observed outcomes and $\beta_\delta$ is correspondingly the log odds-ratio of being observed.

To assess the effect of treatment on the combined outcome we propose a test statistic based on the likelihood ratio statistic
\begin{align}
  W_n(\mu_0, \mu_\delta, s_\mu, \beta_0, \beta_\delta, s_\beta) &= -2 \log \frac{\sup\limits_{\Psi} L_{1,n}(\mu_0, \mu_\delta, s_\mu, \Psi) L_{2,n}(\beta_0, \beta_\delta, s_\beta)}{\sup\limits_{\mu_0, \mu_\delta, s_\mu, \Psi} L_{1,n}(\mu_0, \mu_\delta, s_\mu, \Psi) \sup\limits_{\beta_0, \beta_\delta, s_\beta} L_{2,n}(\beta_0, \beta_\delta, s_\beta)}\label{eq:lrtgeneral}\\
  &= W_{1,n}(\mu_0, \mu_\delta, s_\mu)W_{2,n}(\beta_0, \beta_\delta, s_\beta)
\end{align}

\begin{align}
  W_n^P(\mu_\delta, \beta_\delta) = \sup\limits_{\mu_0, s_\mu} W_{n,1}(\mu_0, \mu_\delta, s_\mu)\sup\limits_{\beta_0, \beta_s} W_{n.2}(\beta_0, \beta_\delta, s_\beta)  \label{eq:LRTtotal}
\end{align}

 use the profile likelihood ratio test statistic which can be written as a function of the treatment effects as
and the value of the likelihood ratio test statistic under the null hypothesis of no treatment effect is therefore $W_n(0, 0)$. Similar to the factorization of the likelihood function in Equation (\ref{eq:likFactorization}), the likelihood ratio test statistic in Equation (\ref{eq:lrtgeneral})  also decomposes into the sum
\begin{align}
  W_n(\mu_\delta, \beta_\delta) &= W_{1,n}(\mu_\delta) + W_{2,n}(\beta_\delta)\label{eq:LRTsum} 
\end{align}
of two likelihood ratio test statistics -- one for the continuous part and one for the discrete part of the combined outcome. Under very general conditions it follows that $W_n(\mu_\delta, \beta_\delta)$ is approximately $\chi^2$ distributed with two degrees of freedom [@wilks1938large; @owen1988empirical].

In order to actually perform the test we still need to decide on an stochastic model for the continuous part of the combined outcome, $Y_i \mid A_i = 1$. In the following two sections we present both a parametric approach based on a normal model and a flexible semi-parametric approach that does not require distributional assumptions.

## Parametric approach {-}

If we combine the model for the expected value in Equation (\ref{eq:glm1}) with the assumption of normal distributed outcomes of the continuous part of the combined outcome we obtain the following sub-model 
\begin{align*}
  Y_i \mid A_i = 1, R_i \sim N\left(\mu_0 + \mu_\delta R_i, \sigma^2\right)
\end{align*}

\begin{align*}
  W_{1,n}(0) = (m_1 + m_2) \log \frac{\widehat{\sigma_0^2}}{\widehat{\sigma^2}}
\end{align*}

With the generalized linear models in Equations (\ref{eq:glm1}) and (\ref{eq:glm2}) the first term is the LRT statistic with a single degree of freedom in a linear regression model, and the second term is the LRT statistic with a single degree of freedom in a logistic regression model. This makes this test very easy to perform in standard statistical software that outputs the likelihood value for a model fit without the need of special methods. The calculation of the likelihood ratio test simply amounts to estimating two linear regression models and two logistic regression models -- for each type a model with and a model without the binary treatment indicator as a covariate. Combining the two likelihood ratios according to Equation (\ref{eq:LRTsum}) calculates our test statistic, and the p-value for no treatment effect can be determined through the $\chi^2$-distribution with two degrees of freedom. The critical value for rejecting the null hypothesis of no treatment effect at the 5% level is equal to $5.99$ and equal to $9.21$ at the 1% level.

A direct consequence of Wilks' theorem [@wilks1938large] is given in the following proposition. Note that the stated conditions are trivially satisfied for an RCT with fixed randomization proportions.

\begin{proposition}
Assume that $P(A_i = 1 \mid R_i = r) > 0$ for $r = 0,1$ and let $m_j = \sum_{i=1}^n 1_{R_i = j}$. Then the parametric profile likelihood ratio test statistic $W_n^P(0,0)$ stated in Equation (\ref{eq:LRTtotal}) for the null hypothesis of no treatment effect on the combined outcome is asymptotically $\chi^2$ distributed with two degrees of freedom for $m_1, m_2 \rightarrow \infty$ and $m_1/m_2 \rightarrow c$ for some finite, positive constant $c$.
\end{proposition}

## Semi-parametric approach {-}

A potential drawback of the parametric likelihood ratio test introduced in the previous section is that it requires deciding on a parametric distribution for the observed outcomes. In this section we introduce a more flexible approach based on an empirical likelihood ratio test. This approach also utilizes the additive decomposition of the likelihood ratio test statistic in Equation (\ref{eq:LRTsum}) but substitutes the term $W_{1,n}$ with a term that is free of any distributional assumptions. Combining this with the binomial model for $A$ leads to a semi-parametric likelihood ratio test for the overall treatment effect.

Let $\mathcal{I}_0 = \left\{i = 1,\ldots, n : R_i = 0, A_i = 1\right\}$ and $\mathcal{I}_1 = \left\{i = 1,\ldots, n : R_i = 1, A_i = 1\right\}$ be the sets of indices of the observed outcomes for the two treatments. The empirical likelihood ratio test statistic as a function of the difference in expected value is given by
\begin{align*}
  W_{1,n}^E(\mu_\delta^\ast) &= 2\sup_{\mu}\left(\sum_{i \in \mathcal{I}_0}\log \left(1 + \lambda_1 (Y_i - \mu)\right) + \sum_{j \in \mathcal{I}_1}\log\left(1 + \lambda_2 (Y_j - \mu - \mu_\delta^\ast)\right)\right)
\end{align*}
where $\lambda_1$ and $\lambda_2$ are the solutions to the following equations
\begin{align*}
  |\mathcal{I}_0|^{-1}\sum_{i \in \mathcal{I}_0} \frac{Y_i - \mu}{1 + \lambda_1 (Y_i - \mu)} = 0, \quad |\mathcal{I}_1|^{-1}\sum_{j \in \mathcal{I}_1}\frac{Y_j - \mu - \mu_\delta^\ast}{1 + \lambda_2 (Y_j - \mu - \beta_\delta^\ast)} = 0
\end{align*}
We refer to the supplementary material for a derivation of this test statistics.

>>>>

The conditional expectation of the combined outcome in Equation (\ref{eq:combinedOutcome}) is given by
\begin{align*}
  E[\widetilde{Y} \mid R, X] = E[Y \mid R, X, A=1]P(A = 1 \mid R, X) + \mathcal{E}P(A = 0 \mid R, X)
\end{align*}
From this expression it can be seen that a treatment comparison expressed in terms of a contrast of the expectation of $\widetilde{Y}$ can be zero even though the distribution of $(Y \mid A=1), A \mid X$  depends on $R$. To see this, let $E[Y \mid A=1, R = 0, X] = \mu(X)$ and $E[Y \mid A=1, R = 1, X] = \mu(X) + \mu_{\delta}(X)$ and assume without loss of generalization that $\mathcal{E} = 0$. Then the average treatment effect for the combined outcome conditional on baseline covariates is 
\begin{align}
  \Delta(X) &= E[\widetilde{Y} \mid R = 1, X] - E[\widetilde{Y} \mid R = 0, X]\label{eq:Delta}\\
        &= \mu(X)\left[P(A = 1 \mid R=1,X) - P(A = 1 \mid R = 0, X)\right] + \mu_{\delta}(X) P(A = 1 \mid R = 1, X)\nonumber
\end{align}
If we auspiciously let $\mu_{\delta}(X) = \mu(X)\left[P(A = 1 \mid R = 0, X) P(A = 1 \mid R = 1, X)^{-1} - 1\right]$ then $\Delta(X) = 0$ for all values of $X$ even though $\mu_{\delta}(X) \ne 0$ and $P(A = 1 \mid R = 0, X) \ne P(A = 1 \mid R = 1, X)$. On the other hand, if $\mu_\delta(X) = 0$ and $P(A = 1 \mid R=1,X) = P(A = 1 \mid R = 0, X)$ then $\Delta(X)$ is necessarily equal to zero. This illustrates that a significance test of no treatment effect must have two degrees of freedom. Such a test which we develop in the subsequent sections is conceptually difference than a test for the null hypothesis $\Delta(X) = 0$.

We propose to test the null hypothesis of no treatment effect on the combined outcome by a likelihood ratio test of the joint distribution of $Y_i \mid A_i$ and $A_i$. This has the advantage that it increases the efficiency compared to the Wilcoxon test and it yields a single p-value appropriate for testing a primary outcome in a clinical trial. Let $(Y_i, A_i, R_i, X_i)$ for $i = 1, \ldots, n$ be independent and identically distributed random variables. We can write our model in a general form as 
\begin{align*}
  Y_i \mid A_i = 1, R_i, X_i &\sim F(Y_i; \mu_i(R_i, X_i), \Psi)\\
  A_i \mid R_i, X_i &\sim \text{Bernoulli}(A_i; \pi_i(R_i, X_i))  
\end{align*}
for some mean functions $\pi_i$ and $\mu_i$ and a distribution function $F$ characterizing the distribution of the observed continuous outcomes with possible nuisance parameters $\Psi$. The joint likelihood function for the combined outcome conditional on treatment and baseline covariates is
\begin{align*}
 L_n(\mu_i(R_i, X_i), \pi_i(R_i, X_i), \Psi) &= \prod_{i=1}^n f(Y_i; \mu_i(R_i, X_i), \Psi)^{A_i}P(A_i = a_i; \pi_i(R_i, X_i))\\
     &= \prod_{i=1}^n f(Y_i; \mu_i(R_i, X_i), \Psi)^{A_i} \pi_i(R_i, X_i)^{A_i} (1 - \pi_i(R_i, X_i))^{1-A_i}\nonumber
\end{align*}
We note that when $F$ has an absolutely continuous density function, $f$, the likelihood function can equivalently be written solely in terms of the combined outcome $\widetilde{Y}$ in Equation (\ref{eq:combinedOutcome}) since $f(Y_i; \cdot)^{A_i} = f(\widetilde{Y}_i; \cdot)^{\mathbbm{1}(\widetilde{Y}_i \ne \mathcal{E})}$ and $\pi_i(\cdot)^{A_i} = \pi_i(\cdot)^{\mathbbm{1}(\widetilde{Y}_i \ne \mathcal{E})}$ almost surely. An important property of this model is that the likelihood function factorizes into two components as
\begin{align*}
 L_n(\mu_i(R_i, X_i), \pi_i(R_i, X_i)) &= L_{1,n}(\mu_i(R_i, X_i), \Psi) L_{2,n}(\pi_i(R_i, X_i))
\end{align*}
where $L_{1,n}(\mu_i(R_i, X_i), \Psi) = \prod_{i=1}^n f(Y_i; \mu_i(R_i, X_i), \Psi)^{A_i}$ and $L_{2,n}(\pi_i(R_i, X_i)) = \prod_{i=1}^n \pi_i(R_i, X_i)^{A_i} (1 - \pi_i(R_i, X_i))^{1-A_i}$. This implies that the parameters for the observed outcomes, $\mu_i(R_i, X_i)$, can be estimated independently of the parameters governing the probability of observing the outcome, $\pi_i(R_i, X_i)$. This factorization is a consequence of the likelihood construction and it does neither assume nor require independence between the value of the outcome and the probability of observing it.

Under the assumption of generalized linear models for $\mu_i(R_i, X_i)$ and $\pi_i(R_i, X_i)$ we may parametrize the conditional mean functions as
\begin{equation}
\begin{aligned}
  \E[Y_i \mid A_i = 1, R_i, X_i] &= \mu_0 + \mu_{\delta} R_i + s_\mu(X_i)\label{eq:glm1}\\
  \logit P(A_i = 1 \mid R_i, X_i) &= \beta_0 + \beta_{\delta} R_i + s_\beta(X_i)
\end{aligned}
\end{equation}
where the treatment effect is quantified by the bivariate contrast $(\mu_\delta, \beta_\delta)$ and $s_\mu, s_\beta\colon\, \mathbb{R}^p \mapsto \mathbb{R}$ are some models for the additional covariates. The parameter $\mu_\delta$ is interpreted as the expected difference among the observed outcomes and $\beta_\delta$ is correspondingly the log odds-ratio of being observed.

To assess the treatment effect on the combined outcome we propose a test statistic based on the likelihood ratio
\begin{equation*}
\begin{aligned}
  W_n(\mu_0, \mu_\delta, s_\mu, \beta_0, \beta_\delta, s_\beta) &= -2 \log \frac{\sup\limits_{\Psi} L_{1,n}(\mu_0, \mu_\delta, s_\mu, \Psi) L_{2,n}(\beta_0, \beta_\delta, s_\beta)}{\sup\limits_{\mu_0, \mu_\delta, s_\mu, \Psi} L_{1,n}(\mu_0, \mu_\delta, s_\mu, \Psi) \sup\limits_{\beta_0, \beta_\delta, s_\beta} L_{2,n}(\beta_0, \beta_\delta, s_\beta)}\label{eq:lrtgeneral}\\
  &= W_{1,n}(\mu_0, \mu_\delta, s_\mu) + W_{2,n}(\beta_0, \beta_\delta, s_\beta)
\end{aligned}
\end{equation*}
where 
\begin{align*}
  W_{1,n}(\mu_0, \mu_\delta, s_\mu)  &= -2\left(\log \sup\limits_{\Psi} L_{1,n}(\mu_0, \mu_\delta, s_\mu, \Psi) - \log \sup\limits_{\mu_0, \mu_\delta, s_\mu, \Psi} L_{1,n}(\mu_0, \mu_\delta, s_\mu, \Psi)\right)\\
  W_{2,n}(\beta_0, \beta_\delta, s_\beta) &= -2\left(\log L_{2,n}(\beta_0, \beta_\delta, s_\beta) - \log \sup\limits_{\beta_0, \beta_\delta, s_\beta} L_{2,n}(\beta_0, \beta_\delta, s_\beta) \right)
\end{align*}
are the likelihood ratio test statistics for each of the components. As a test statistic we use the profile likelihood ratio defined as
\begin{align}
  W_n^P(\mu_\delta, \beta_\delta) = \sup\limits_{\mu_0, s_\mu} W_{1,n}(\mu_0, \mu_\delta, s_\mu) + \sup\limits_{\beta_0, s_\beta} W_{2,n}(\beta_0, \beta_\delta, s_\beta)  \label{eq:LRTtotal}
\end{align}
which is only a function of the two treatment contrasts. Specifically, for the null-hypothesis of no treatment effect the test statistic $W_n^P(0, 0)$ is used.

In the following we will consider both a parametric and a semi-parametric version of our profile likelihood ratio. The difference between the two are that the parametric test assumes a specific distributional form for $W_{n,1}(\mu_0, \mu_\delta, s_\mu)$, e.g., for $Y_i \mid A_i = 1, R_i, X_i$ the continuous part of the model, while the semi-parametric version is based on a profile empirical likelihood ratio and does not require any distributional assumptions.

If we combine the model for the conditional expectation of observed outcomes in Equation (\ref{eq:glm1}) with the assumption of normality we obtain the following sub-model 
\begin{align*}
  Y_i \mid A_i = 1, R_i, X_i \sim N\left(\mu_0 + \mu_\delta R_i + s_\mu(X_i), \sigma^2\right)
\end{align*}
which gives rise to a parametric form of $L_{1,n}$ and thereby $W_{1,n}(\mu_0, \mu_\delta, s_\mu)$. Plugging the latter into Equation (\ref{eq:LRTtotal}) yields our proposed parametric likelihood ratio test. We note any parametric model other than the normal distribution can also be used.

A direct consequence of Wilks' theorem [@wilks1938large] is the large sample distribution of $W_n^P(0, 0)$ which leads to the following proposition.

\begin{proposition}
Assume that $P(A_i = 1 \mid R_i = r) > 0$ for $r = 0,1$ and let $m_j = \sum_{i=1}^n \mathbbm{1}(R_i = j)$. Then the parametric profile likelihood ratio test statistic $W_n^P(0,0)$ stated in Equation (\ref{eq:LRTtotal}) for the null hypothesis of no treatment effect on the combined outcome is asymptotically $\chi^2$ distributed with two degrees of freedom for $m_1, m_2 \rightarrow \infty$ and $m_1/m_2 \rightarrow c$ for some finite, positive constant $c$.
\end{proposition}

We note that given specific models for $s_\mu(X_i)$ and $s_\beta(X_i)$ this parametric likelihood ratio test is particularly simple to calculate in standard statistical software. One estimates two linear regression models and two logistic regression model with and without the binary treatment indicator as covariate and add their individual log likelihood differences according to Equation (\ref{eq:LRTtotal}). The p-value for no treatment effect can then be determined through the $\chi^2$-distribution with two degrees of freedom. The critical value for rejecting the null hypothesis of no treatment effect at the 5% level is thus equal to $5.99$ and equal to $9.21$ at the 1% level.

A potential drawback of the parametric likelihood ratio test is that it relies on a distributional model for the observed outcomes. In this section we introduce a more flexible approach based on an empirical likelihood ratio test. This approach also utilizes the additive decomposition of the likelihood ratio test statistic in Equation (\ref{eq:LRTtotal}) but substitutes the term $W_{1,n}$ with a term that is free of any distributional assumptions. Combining this with the binomial model for $A \mid R_i, X_i$ in the $W_{2,n}$ leads to a semi-parametric likelihood ratio test for the overall treatment effect.

Let $\mathcal{I}_0 = \left\{i = 1,\ldots, n : R_i = 0, A_i = 1\right\}$ and $\mathcal{I}_1 = \left\{i = 1,\ldots, n : R_i = 1, A_i = 1\right\}$ be the sets of indices of the observed outcomes for the two treatment groups. As derived in the supplementary material, the empirical likelihood ratio test statistic as a function of the difference in expected value is given by
\begin{align*}
  W_{1,n}^E(\mu_\delta^\ast) &= 2\sup_{\mu}\left(\sum_{i \in \mathcal{I}_0}\log \left(1 + \lambda_1 (Y_i - \mu)\right) + \sum_{j \in \mathcal{I}_1}\log\left(1 + \lambda_2 (Y_j - \mu - \mu_\delta^\ast)\right)\right)
\end{align*}
where $\lambda_1$ and $\lambda_2$ are the solutions to the following equations
\begin{align*}
  |\mathcal{I}_0|^{-1}\sum_{i \in \mathcal{I}_0} \frac{Y_i - \mu}{1 + \lambda_1 (Y_i - \mu)} = 0, \quad |\mathcal{I}_1|^{-1}\sum_{j \in \mathcal{I}_1}\frac{Y_j - \mu - \mu_\delta^\ast}{1 + \lambda_2 (Y_j - \mu - \beta_\delta^\ast)} = 0
\end{align*}
We refer to the supplementary material for a derivation of this test statistics.
